\cvsection{Professional Experience}

\begin{cventries}
  \cventry
    {Backend Team Lead}
    {Superapp Backend}
    {Ozan}
    {August 2023 – Present}
    {
      \begin{cvitems}
        \item {Lead a remote backend team, managing task allocation, backlog analysis, and sprint planning for timely, high-quality delivery.}
        \item {Architect and manage the development of microservices tailored for fintech applications, leveraging Java, Spring Boot, and PostgreSQL to ensure regulatory compliance and scalability.}
        \item {Resolve technical challenges and optimize communication across cross-functional teams, enhancing backend efficiency and fostering cross-team collaboration.}
        \item {Implemented task prioritization and agile methodologies to streamline development cycles and improve operational efficiency across the team.}
      \end{cvitems}
    }

  \cventry
    {Senior Software Developer}
    {Superapp Backoffice}
    {Ozan}
    {December 2022 – August 2023}
    {
      \begin{cvitems}
        \item {Spearheaded the development of the BFF (Backend for Frontend) layer using Nest.js, TypeScript, and GraphQL, streamlining data handling and optimizing frontend-backend integrations for faster response times.}
        \item {Enhanced system adaptability and minimized debugging and maintenance costs by creating a developer-friendly architecture that facilitated rapid onboarding.}
        \item {Streamlined data handling processes to optimize application performance, contributing to lower latency and improved user experience across the back-office platform.}
        \item {Collaborated closely with cross-functional teams to align backend capabilities with evolving business requirements, ensuring seamless integration and system scalability.}
      \end{cvitems}
    }

  \cventry
    {Software Architect}
    {Mobile Search \& Chatbot}
    {Akbank}
    {November 2020 – December 2022}
    {
      \begin{cvitems}
        \item {Architected and developed backend solutions for Akbank's Chatbot product using Microsoft Bot Framework, enabling responsive, user-friendly interactions within the mobile application.}
        \item {Optimized ETL processes to ensure continuous and efficient data flow, optimizing search engine performance and data processing efficiency and improving search accuracy and response times.}
        \item {Played a key role in recruitment efforts, conducting technical interviews to assess and onboard qualified candidates, strengthening the team's technical capabilities.}
        \item {Collaborated with cross-functional teams to design scalable, reliable solutions that met both technical and business goals, ensuring consistent alignment with Akbank's strategic objectives.}
      \end{cvitems}
    }

  \cventry
    {Senior Software Specialist}
    {D-Filo}
    {Doğuş Teknoloji}
    {September 2020 – November 2020}
    {
      \begin{cvitems}
        \item {Contributed to the setup and development of the D-Filo fleet management solution for Doğuş Otomotiv.}
        \item {Played a key role in designing the infrastructure and backend system from scratch.}
      \end{cvitems}
    }

  \cventry
    {Senior Software Specialist}
    {VDF Filo}
    {Doğuş Teknoloji}
    {April 2016 – September 2020 (excl. 2018)}
    {
      \begin{cvitems}
        \item {Contributed to the development of the VDF Filo fleet management system, working on modules such as invoicing, operations, and collections.}
        \item {Developed the backend using .NET Core, with the frontend built using TypeScript and the database managed on MSSQL.}
        \item {Led the second phase of the project, focusing on DevOps needs, improving deployment pipelines, and ensuring effective collaboration between teams.}
        \item {Supported the project through continuous new feature development and enhancements to improve operational efficiency.}
      \end{cvitems}
    }

  \cventry
    {Software Specialist}
    {NTV \& NTV Spor}
    {Doğuş Teknoloji}
    {September 2018 – December 2018}
    {
      \begin{cvitems}
        \item {Explored modern technologies and NoSQL databases while contributing to the development of applications for NTV and NTV Spor.}
        \item {Short-term project due to the termination of the contract between Doğuş Yayın Grubu and Doğuş Teknoloji.}
      \end{cvitems}
    }

  \cventry
    {Software Specialist}
    {Doğuş İnşaat ERP}
    {Doğuş Teknoloji}
    {January 2018 – September 2018}
    {
      \begin{cvitems}
        \item {Redesigned key ERP screens to improve user experience and streamline data input processes.}
        \item {Developed and optimized reporting modules, enhancing the accuracy and speed of financial and operational reporting.}
      \end{cvitems}
    }

  \cventry
    {Software Developer}
    {Leaseplan ERP}
    {Doğuş Teknoloji}
    {July 2013 – April 2016}
    {
      \begin{cvitems}
        \item {Full-stack development for the vehicle fleet rental ERP system, with a focus on backend work using .NET Framework and MSSQL.}
        \item {Developed essential modules for the system while also contributing to frontend tasks in JavaScript.}
      \end{cvitems}
    }

\end{cventries}
