\cvsection{Personal Projects}

\begin{cventries}
  \cventry
    {Developer}
    {Focus Blocker}
    {Chrome Web Store}
    {January 2023 – January 2024}
    {
      \begin{cvitems}
        \item {Developed a Google Chrome extension designed to help users minimize online distractions and stay focused during work sessions.}
        \item {Implemented features that allow users to block specified websites and content, promoting a more productive browsing experience.}
        \item {Provided customizable settings for users to adjust restrictions based on their individual productivity needs.}
      \end{cvitems}
    }

  \cventry
    {Open-source Contributor}
    {ThinkThread – Open Source Community}
    {npm}
    {October 2023 – November 2023}
    {
      \begin{cvitems}
        \item {Developed and published multiple npm packages aimed at assisting Node.js developers in various tasks.}
        \item {Focused on creating accessible, well-documented packages that enhance productivity and streamline development workflows.}
        \item {Maintained and updated packages based on community feedback and evolving best practices.}
      \end{cvitems}
    }

  \cventry
    {Developer}
    {Smart Forecast}
    {Shopify}
    {August 2022 – September 2022}
    {
      \begin{cvitems}
        \item {Created a Shopify plugin to offer sales-boosting recommendations based on product analytics.}
        \item {Built the plugin to integrate seamlessly with Shopify stores, enabling owners to enhance sales with data-driven insights.}
        \item {Optimized for ease of use, providing actionable advice without the need for extensive configuration.}
      \end{cvitems}
    }

  \cventry
    {Developer}
    {Messagine Bot}
    {Telegram}
    {January 2021 – April 2021}
    {
      \begin{cvitems}
        \item {Developed a Telegram bot that allows users to engage in anonymous conversations in their preferred language.}
        \item {Designed and implemented multilingual functionality, removing the need for identity verification.}
        \item {Focused on user privacy and seamless integration with Telegram's API for an intuitive experience.}
      \end{cvitems}
    }

\end{cventries}
