\resumeSubheading
  {Backend Team Lead · Superapp Backend}
  {Ozan}
  {Remote · Antalya, Turkey}
  {August 2023 -- Present}
\begin{itemize}
  \item Lead a remote backend team, driving sprint planning, backlog prioritization, and delivery commitments for fintech products.
  \item Architect microservices with Java, Spring Boot, and PostgreSQL to meet regulatory requirements while scaling securely.
  \item Remove blockers across cross-functional teams and streamline agile practices to reduce cycle times and improve team throughput.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Senior Software Developer · Superapp Backoffice}
  {Ozan}
  {Istanbul \& Remote}
  {December 2022 -- August 2023}
\begin{itemize}
  \item Built and maintained the Backend for Frontend layer with Nest.js, TypeScript, and GraphQL to unify external integrations.
  \item Simplified application debugging and onboarding by introducing developer-centric architecture patterns and documentation.
  \item Minimized latency and optimized data flows, directly improving response times for back-office operations.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Software Architect · Mobile Search \& Chatbot}
  {Akbank}
  {Istanbul, Turkey}
  {November 2020 -- December 2022}
\begin{itemize}
  \item Led backend design and development of Akbank's chatbot using Microsoft Bot Framework, improving conversational UX.
  \item Tuned ETL pipelines and search indexing to increase accuracy and responsiveness for mobile search experiences.
  \item Participated in recruiting and technical interviews to strengthen engineering capabilities across the organization.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Senior Software Specialist · D-Filo}
  {Doğuş Teknoloji}
  {Istanbul, Turkey}
  {September 2020 -- November 2020}
\begin{itemize}
  \item Co-designed the infrastructure and backend platform for a new fleet management solution from the ground up.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Senior Software Specialist · VDF Filo}
  {Doğuş Teknoloji}
  {Istanbul, Turkey}
  {April 2016 -- September 2020 (excluding 2018)}
\begin{itemize}
  \item Engineered core fleet-management modules covering invoicing, operations, and collections using .NET Core and TypeScript.
  \item Led DevOps initiatives for the second project phase, hardening CI/CD pipelines and automating deployments.
  \item Drove continuous enhancements that boosted operational performance and reliability.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Software Specialist · NTV \& NTV Spor}
  {Doğuş Teknoloji}
  {Istanbul, Turkey}
  {September 2018 -- December 2018}
\begin{itemize}
  \item Explored emerging technologies and NoSQL data stores while delivering media applications for NTV and NTV Spor.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Software Specialist · Doğuş İnşaat ERP}
  {Doğuş Teknoloji}
  {Istanbul, Turkey}
  {January 2018 -- September 2018}
\begin{itemize}
  \item Redesigned ERP interfaces and streamlined reporting workflows to improve data accuracy and usability.
\end{itemize}
\vspace{0.3em}

\resumeSubheading
  {Software Developer · Leaseplan ERP}
  {Doğuş Teknoloji}
  {Istanbul, Turkey}
  {July 2013 -- April 2016}
\begin{itemize}
  \item Delivered full-stack features for a vehicle fleet rental ERP platform using .NET Framework, MSSQL, and JavaScript.
\end{itemize}
